---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(funique)
```
# funique

A faster `unique()` function

## Installation

You can install the released version of funique from Github with:

``` r
## install from github
devtools::install_github("mkearney/funique")
```

## Usage

There's one function `funique()`, which is the same as `base::unique()` only optimized to be faster when data contain date-time variables.

## Speed test: `funique()` vs. `base::unique()`

The code below creates a data frame with several duplicate rows and then compares performance (in time) of `funique()` versus `base::unique()`.

```{r ex1}
## create data set with a date-time column
d <- datasets::mtcars
d$dttm <- Sys.time() + runif(nrow(d), -1000, 1000)

## create multiple data frames with duplicate rows
d <- lapply(1:50, function(.) rbind(d, d[sample(seq_len(nrow(d)), 20), ]))
## merge into single data frame
d <- do.call("rbind", d)

## compare times between funique() and base::unique()
library(microbenchmark)

## benchmarks
(mb <- microbenchmark(unique(d), funique(d), unit = "relative"))

## make sure the output is the same
identical(unique(d), funique(d))

## plot
plot(mb)
```

Here's another test this time using duplicate-infested Twitter data.

```{r ex2}
## search for data on 1,000 tweets
rt <- rtweet::search_tweets("lang:en", n = 500, verbose = FALSE)

## create duplicates
rt2 <- rbind(rt, rt[sample(1:nrow(rt), 100), ])

## benchmarks
(mb <- microbenchmark(unique(rt2), funique(rt2), unit = "relative"))

## make sure the output is the same
identical(unique(rt2), funique(rt2))

## plot
plot(mb)
```

